Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-25 Ben_Manuscripts/structure_paper/supporting_information.tex
Revisions and new figures

  We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
  generated using Packmol (\cite{martinez_packmol:_2009}). The input file given to 
  Packmol is shown below.
  \lstset{language=bash}
  \begin{lstlisting}
  tolerance 2.0
  output packed.pdb
  filetype pdb
  structure monomer.pdb
  		number 400
  		inside box 0. 0. 0. 84.3 84.3 84.3
  end structure
  \end{lstlisting}

  We used the same number of monomers (400) that we used in all other simulations. 
  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
  box with a volume of 660 $nm^3$, 25 \% larger than those used to create ordered unit
  cells we studied.

  We use the nematic order paramter as defined in section~\ref{method:nematic_order} to 
  observe any progress towards an system ordering.

  %BJC: picture of isotropic box (before and after?)
  %BJC: plot of nematic order parameter vs. time

@@

>>>>

  We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
  generated using Packmol \cite{martinez_packmol:_2009} (Figure~\ref{fig:isotropic_box}).
  The input file given to Packmol is shown below.

  \lstset{language=bash}
  \begin{lstlisting}
  tolerance 2.0
  output packed.pdb
  filetype pdb
  structure monomer.pdb
  		number 400
  		inside box 0. 0. 0. 84.3 84.3 84.3
  end structure
  \end{lstlisting}

  We used the same number of monomers (400) that we used in all other simulations. 
  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
  box with a volume of 660 $nm^3$, 25 \% larger than those used to create ordered unit
  cells we studied. We tested systems with semiisotropic and anisotropic pressure 
  coupling since the shape of the unit cell will likely need to change in order to 
  accomodate hexagonally packed pores.

  We use the nematic order paramter as defined in section~\ref{method:nematic_order} to 
  observe any progress towards system ordering. In both cases, we see that the nematic
  order parameter stays close to zero for the duration of the simulation time, indicating
  an isotropic arrangement of head groups (Figure~\ref{fig:nematic_isotropic}). The values
  are slightly negative since there are only 400 monomers. 
  Equation~\ref{eqn:nematic_order_parameter} is bounded between -1 and 1, however, with a
  proper choice of nematic director, measured values will range between 0 and 1. With a 
  large number of samples, an isotropic system would have an order parameter of 0.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{isotropic_box.png}
  \caption{}\label{fig:isotropic_box}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nematic_isotropic.png}
  \caption{}\label{fig:nematic_isotropic}
  \end{subfigure}
  \caption{(a) We created a box of isotropically packed monomers and allowed it to simulate
  for 100 ns using isotropic and anisotropic pressure coupling. (b) The nematic order 
  parameter hovers close to zero for the duration of the simulation meaning the system
  maintains its isotropic alignment.}\label{fig:self_assembly}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{carboxylate_dihedral_rb.png}
  \caption{A potential energy diagram for the dihedral angle about the carbon-carbon bond of
  a carboxylate group attached to an aromatic ring, using parameters from the generalized amber 
  forcefield. It is energetically favorable for the carboxylate group to stay in plane with 
  the aromatic ring. There is a large energy penalty as the dihedral becomes antiparallel to 
  the plane of the aromatic ring.}\label{fig:carboxylate_dihedral_rb}
  \end{figure}
